---
title: "Help"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Help}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(StatComp21037)
```

The first function cv takes three arguments: df, a data frame with a default of prostate cancer measurements; k, an integer determining the number of crossvalidation folds, with a default of 5; and seed, an integer to be passed to set.seed() before defining the folds, with a default of NULL (meaning no seed shall be set). 

This function splits up the given data df into k folds of roughly equal size, and using these folds, compute the cross-validation error of the linear model that is given by the formula.str with a default of regressing lpsa on lcavol and lweight. Its output is the cross-validation error under the given linear regression model. 

The feature of this function is that the linear model is also an input choice. That makes this cv function much more flexible and useful in different cases. 

The second function ce takes two arguments: xdata, a dataframe with 2 cols and alpha. This function helps draw a confidence ellipse of binary normal distribution data. 